% Adapted from layout by Jake Vanderplas
% https://github.com/jakevdp/website/tree/master/CV
%

\documentclass{article} %{{{--
\usepackage[paper=a4paper,
	    top=2cm,
	    left=1.35cm,
	    width=18.2cm,
	    bottom=2cm,
	    ]{geometry}
            %margin=4cm,
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage{calc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[pdftex,  % needed for pdflatex
  breaklinks=true,  % so long urls are correctly broken across lines
  colorlinks=true,
  urlcolor=myblue]{hyperref}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{multicol}
\usepackage{wasysym} % For phone symbol
\usepackage{url}
\usepackage{marvosym}

\def\bf{\bfseries}
\def\sf{\sffamily}
\def\sl{\slshape}
% Semi condensed bold

\definecolor{deep_blue}{rgb}{0,.2,.5}
\definecolor{dark_blue}{rgb}{0,.1,.3}
\definecolor{myblue}{rgb}{.01,0.21,0.71}
\definecolor{gray}{rgb}{.5, .5, .5}


%% This gives us fun enumeration environments. 
\usepackage{enumitem}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% Reference the last page in the page number
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
%\fancyfootoffset{\marginparsep}+\marginparwidth}
\lfoot{
  \hspace{-2\marginparsep}
  \,\hfill \arabic{page} of \protect\pageref*{LastPage}  \hfill \,\\
  \,\hfill {\footnotesize \textcolor{gray}{updated February 2021~~~~~}} \hfill\,
}

\newcommand{\mydate}[1]{{\textcolor{gray}{\footnotesize #1}}}


\newcommand{\makeheading}[1]%
        {%\hspace*{-\marginparsep minus \marginparwidth}%
         %\begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
         \begin{minipage}[t]{\textwidth}%
                {\Large #1}\\%[-0.5\baselineskip]%
                \vskip 0.2\baselineskip
                 \color{deep_blue}{\rule{\columnwidth}{3pt}}%
         \end{minipage}
	 \vskip 1.\baselineskip plus 2\baselineskip minus 1.\baselineskip
	}

\newlength\sidebarwidth
\setlength\sidebarwidth{3.6cm}

\newcommand{\topic}[3][]%
	 {\pagebreak[2]%
	 \vskip 1.5\baselineskip plus 3\baselineskip minus 0.7\baselineskip
	 \begin{minipage}{\textwidth}
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft \bf\sf 
	 \color{deep_blue}{\Large #2}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 \nopagebreak{\color{deep_blue}%
		    \rule{0pt}{\baselineskip}%
		    \rule{\linewidth}{2.5pt}%
		    \llap{\raisebox{.3\baselineskip}{\sf #1}}%
		    \vspace*{.1\baselineskip}%
		    }%
	 #3%
	 \end{minipage}
	 \end{minipage}}

\newcommand{\smalltopic}[2]%
	 {\pagebreak[2]%
	 \vskip 1\baselineskip plus 2\baselineskip minus 0.3\baselineskip
	 \begin{minipage}{\textwidth}
	 %\hspace{-\marginparsep minus \marginparwidth}%
         \phantomsection\addcontentsline{toc}{subsection}{#1}%
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft \bf\sf %\vskip -0.5\baselineskip
	 \textcolor{dark_blue}{\large #1}%
	 \end{minipage}%+
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 \nopagebreak{%
	    %\vspace{-.7\baselineskip}%
	    \rule{\linewidth}{.5pt}%
	    \vspace{.1\baselineskip}%
	    }%
	    #2
	 \end{minipage}
	 \end{minipage}}

\newcommand{\subtopic}[3][]
	 {\begin{minipage}{\textwidth}
	 \vspace*{.4\baselineskip}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
	 % Super posh: using semi-bold condensed fonts. Works only with
	 % lmodern
         \raggedleft {\sf\fontseries{sbc}\selectfont #2}
	 %{\small\sl\\[-0.2\baselineskip] #1}
         {\\[-0.2\baselineskip] \textcolor{gray}{\footnotesize #1}}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #3%
	 \end{minipage}%
	 \vspace*{.2\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

\newcommand{\dateonly}[2][]
	 {\begin{minipage}{\textwidth}
	 \vspace*{.4\baselineskip}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft {~}
         {\\[-\baselineskip] \textcolor{gray}{\footnotesize #1}}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #2%
	 \end{minipage}%
	 \vspace*{.2\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

\newcommand{\sidenote}[2]
	 {\vspace*{-.2\baselineskip}\begin{minipage}{\textwidth}
         \nopagebreak\hspace{0in}%
         \nopagebreak\begin{minipage}[t]{\sidebarwidth - .2cm}
         \raggedleft {#1}
	 \end{minipage}%
	 \hfill
	 \begin{minipage}[t]{\linewidth - \sidebarwidth}
	 #2%
	 \end{minipage}%
	 \vspace*{.5\baselineskip plus 1\baselineskip minus
	 .2\baselineskip}%
	 \end{minipage}}

% New lists environments 
\newlist{outerlist}{itemize}{1}
\setlist[outerlist]{font=\sffamily\bfseries, label=\textbullet}
\setitemize{topsep=0ex, partopsep=0ex}
\setdescription{font=\normalfont\sffamily\bfseries, itemsep=.5ex,
    parsep=.5ex, leftmargin=3ex}

\newcommand{\blankline}{\quad\pagebreak[2]}

\def\mydot{\textcolor{deep_blue}{\rule{1ex}{1ex}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%--}}}%
\begin{document}
\makeheading{
\begin{minipage}[B]{0.5\textwidth}
    %\vfill
    \vspace*{-.5\baselineskip}%
    \parbox{10cm}{
	\hskip -0.1cm
	{\textcolor{gray}{\huge{\textsl{\textsf{Curriculum Vitae}}}}}
	\hskip -0.1cm
	\vspace{0.25 cm}
	\\
	{\Huge\bf\sf \color{deep_blue} M\huge \hskip -0.05cm IKKO %
	 \Huge \color{deep_blue} L\huge \hskip -0.05cm EPPÄNEN}
	\\[-.1\baselineskip]
    }
\end{minipage}
\hfill
\begin{minipage}[B]{8cm}
    \raggedleft
    \,\vskip -3em
    \small
        Kivimiehentie 2B \\
        04300 Tuusula \\
        Finland \\
        {\textcolor{blue}\Mobilefone} \textsf{+358 50 408 7703}\\
	      {\textcolor{blue}\Email} \texttt {mleppan23@gmail.com}\\
	      \href{https://www.linkedin.com/in/mikko-lepp\%C3\%A4nen-05bb621a/}{LinkedIn Profile}\\
	      \href{https://www.linkedin.com/in/mikko-lepp\%C3\%A4nen-05bb621a/}{Github Profile}%
\end{minipage}
}

%\begin{center} 
%\begin{minipage}{15cm}
\begin{multicols}{2}
\sloppy

%\textcolor{deep_blue}{\bf\sf Research interests}:
%Cosmology, weak lensing, data mining and automated learning algorithms for
%large astronomical data sets.

\begin{itemize}[leftmargin=2ex, itemsep=0ex]
\item[\mydot]
I currently work as a Chief Design Engineer Software Test Automation at KONE.
\item[\mydot]
I always strive for perseverance. My working morale is very high and I am committed on what I am doing. I always work relentlessly and hard to achieve my goals. I work thoroughly with high respect on deadlines. 
\item[\mydot]
I have a passion for learning. I constantly try to improve my skills and learn new things and technologies. I enjoy creating software that is clean, functional and elegant. I believe that applying refactoring techniques, test-driven development and SOLID principles help me to achieve that. This is what motivates me and pushes me to work harder. I also have taken on-line courses on some topics I find interesting, like Full-Stack development, a new programming language or machine learning. I've always been curious and jump at the opportunity to gain some new interesting experience or taking a new challenge. This is what motivates me and pushes me to work harder.

\item[\mydot]
My next movement is full-stack development. Achieving this goal I have focuced on several technologies during the last year. Some buzzwords are JavaScript, Node.js, React, MongoDB, TypeScript, Django, FastAPI, Webpack, Golang, API design, Docker (containers), Kubernetes.

\item[\mydot]
Over 10 years of experience in industry has taught me how to build relationships and how to communicate and get along with different types of people. I am good working within a team and independently. I always try to share my ideas as well as helping other co-workers. As a worker I am unprompted and systematic. My professional strengths are on the fields of test automation and software development.


\end{itemize}
\end{multicols}
\vspace*{-1.5em}
\fussy
%\end{minipage}
%\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{E \large\hskip -1ex DUCATION}{~}

    \subtopic[2003-2009]{\bf M.Sc.}{
        Tampere University of Technology \\
        Electrical Engineering(Electromagnetics)\\
    }

    \subtopic[1999-2002]{\ }{
      Upper Secondary School of Kangasala\\
    }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{E \large\hskip -1ex XPERIENCE}{~}

\vspace*{-0.5\baselineskip}
\smalltopic{Employment}{}

    \subtopic[2020--Present]{KONE}{
      Chief Design Engineer, Software Test Automation \\
      Implementing test automation for lift features. Design and develop test automation solutions and maintain code base. Acting as a Scrum Master of the design team.
      Keywords: Test Automation, Robot Framework, Python, Embedded Systems, DevOps, CI/CD, Hardware/Software, Agile.
      }
      
    \subtopic[2019--2020]{Etteplan}{
      Software Test Automation Specialist, Software Testing \\
      Implementing test automation for customer projects. Design and develop test automation solutions and maintain code base.
      Keywords: Test Automation, Robot Framework, Python, Embedded Systems, DevOps, CI/CD, Hardware/Software
      }
      
    \subtopic[2019--2019]{Siili Solutions}{
      RPA and Python Developer, Intelligent Automation \\
      Designing cloud based RPA solutions for customers using open source software. Technology toolset consists of Python, Robot Framework, Jenkins and AWS.
      }
    \subtopic[2018--2019]{KONE}{
      Software Test Automation Specialist, Software Testing \\
      Software test automation using Robotframework and Python for lift appications including Iot devices and KONE Connected 24/7 products.
      Also my responsibilities included code reviews, refactoring and developing test library code base, test case planning and maintaining test equipment.
      }
  
    \subtopic[2016--2018]{KONE}{
      Software Test Engineer, Software Testing \\
      Software release testing and debugging using lift simulators.}

    \subtopic[2014--2016]{KONE}{
      R\&D Design Engineer, Electrical Machines \\
      Elevator motor/machinery testing and testing hardware/application development using Matlab/Python}

    \subtopic[2008--2014]{Vacon Plc}{
      R\&D Development Engineer \\
      Main circuit design, mainly responsible for inductive and capacitive components.
In addition, performing different modeling tasks(electromagnetics/thermal design)
and matlab programming.}

    \subtopic[2007--2008]{TUT}{
      Research Assistant\\
      Tampere University of Technology}

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{K \large\hskip -1ex NOWHOW}{}

\vspace*{-0.5\baselineskip}
\smalltopic{Skills}{
  \begin{itemize}[leftmargin=0ex, itemsep=0ex, labelindent=-2ex, parsep=.5ex]
    \item[\mydot] Programming/Scripting: Python, JavaScript, Modern C++, MATLAB, Golang, TypeScript
    \item[\mydot] DevOps: Robot Framework, Git, Jenkins, Ansible, Vagrant, Docker
    \item[\mydot] Database: SQLite, MongoDB, SQLAlchemy, PostgreSQL 
    \item[\mydot] Cloud: AWS
    \item[\mydot] Technologies: Qt/QML, GCC, LLVM/Clang, Boost, STL, React, Node.js   
    \item[\mydot] Tools: PyCharm, QtCreator, VSCode, Mypy
    \item[\mydot] Experience with bash, \LaTeX{}, HTML5, CSS
    \item[\mydot] Operating systems: Linux (Ubuntu), Windows 10
  \end{itemize}
}

\smalltopic{Scientific simulation software}{}
   \subtopic[]{Ansys Maxwell}{
     I have used Maxwell electromagnetic field simulation software
     many years for various engineering tasks.}

   \subtopic[]{Ansys Icepak}{
     I have used Icepak for a few years. I have done several different 
     kind of thermal simulations for the AC drives. In addition I have participated 
     in several trainings and seminars related to Icepak/thermal engineering.  
   }

   \subtopic[]{Ansys Simplorer}{
     I have used Simplorer for the AC drives simulation.
   }

   \subtopic[]{Ansys Q3D}{
     I have some experience with Q3D related to busbar simulations.  
   }
   
  %For more information, see my Github and Matlab Central File Exchange profiles:\\
  %\href{http://www.mathworks.com/matlabcentral/fileexchange/authors/125461}
  %{http://www.mathworks.com/matlabcentral/fileexchange/authors/125461}\\
  %\href{https://github.com/mikeleppane}{https://github.com/mikeleppane}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{C \large\hskip -1ex OURSES}{~}

    \subtopic[]{Talk Python Training - Courses}{
        Full Web Apps with FastAPI\\
        Modern APIs with FastAPI and Python\\
        Python Memory Management and Tips\\
        Building Data-Driven Web Apps with Flask and SQLAlchemy\\
        Async Techniques and Examples in Python\\
        100DaysOfWeb in Python\\
        Mastering PyCharm\\
        MongoDB for Developers with Python
    }
    \subtopic[]{FrontendMasters - Courses}{
        JavaScript: The New Hard Parts\\
        Deep JavaScript Foundations\\
        Complete Intro to Containers\\
        Go for JavaScript Developers\\
        JavaScript Performance \\
        Introduction to Node.js \\
        TypeScript 3 Fundamentals \\
        Introduction to MongoDB \\
        State Management in Pure React \\
        Intermediate React \\
        API Design in Node.js \\
        JavaScript: The Recent Parts
    }
    \subtopic[]{Oreilly - Online Training}{
        Ultimate Go Programming \\
        Scrum Fundamentals \\
        Enterprise Software with Python \\ 
        Python Django Dev To Deployment \\
        Clean Code Applied (Clean Coders Video Series): Building a Java Web Application with Software Craftsmanship \\
        Clean Coder (Clean Coders Video Series) \\
        Advanced Web Development in Python with Django \\
        Scrum Fundamentals and Advanced \\
        Web Development in Python with Django: Building Backend Web Applications and APIs with Django \\ 
        Python Programming Language \\
        Modern Python LiveLessons: Big Ideas and Little Code in Python
    }
    \subtopic[]{Udemy - Courses}{
        Docker Mastery: with Kubernetes + Swarm \\
        Typescript: The Complete Developer's Guide \\
        Django 3 - Full Stack Websites with Python Web Development \\
        Understanding TypeScript \\
        Modern React with Redux \\
        React - The Complete Guide (incl Hooks, React Router, Redux) \\
        JavaScript - The Complete Guide \\ 
        Node JS: Advanced Concepts \\ 
        Clean Code \\
        React and Django: A Practical Guide with Docker \\ 
        MongoDB - The Complete Developer's Guide \\  
        Node with React: Fullstack Web Development \\
        NodeJS - The Complete Guide (MVC, REST APIs, GraphQL, Deno)
    }
    
    
    \subtopic[2019]{A Cloud Guru}{
       AWS Certified Solutions Architect Associate 2019\\
    }
    
    \subtopic[2014]{XSPIS}{
      Cross platform application development using Qt framework\\
    }
    
    \subtopic[2014]{XSPIS}{
       Become a Developer for Sailfish Operating System: An Introduction \\
    }
    \subtopic[2014]{Coursera}{
       High Performance Scientific Computing course \\
    }
    
    \subtopic[2011]{ECPE}{
        ECPE/Cluster Tutorial: Part 1 - Thermal Engineering of Power Electronic Systems (Thermal Design and           
        Verification) - Erlangen, Germany\\
    }

    \subtopic[2011]{ECPE}{
      ECPE/Cluster Tutorial: Part 2 - Thermal Engineering of Power Electronic Systems (Thermal Management and
      Reliability) - Erlangen, Germany\\
    }
    
    
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topic{P \large\hskip -1ex ERSONAL DETAILS}{~}

    \subtopic[]{\ }{
        Place of Birth: Loviisa, Finland\\
        Nationality: Finnish\\
        Military Service: July 2002 -- July 2003\\
    }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\topic{H \large\hskip -1ex OBBIES}{~}

%    \subtopic[]{\ }{
%        Mountain biking \\
%        Indoor rowing \\
%        Programming\\
%        Gym \\
%        Badminton
%    }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
